---
title: "BasicCellPaintAnalysis"
author: "David James"
date: "22/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(data.table)
library(ggplot2)
library(reshape2)
library(caret)
source("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/RScripts_011122/cellPaintFunctions.r")
```

## Features to remove
```{r}
# Features to remove (because of NA columns or location parameters)
NACols <- c("AreaShape_NormalizedMoment_0_0_nuc", "AreaShape_NormalizedMoment_0_1_nuc",  "AreaShape_NormalizedMoment_1_0_nuc",  "AreaShape_NormalizedMoment_0_0_cell",
 "AreaShape_NormalizedMoment_0_1_cell", "AreaShape_NormalizedMoment_1_0_cell", "AreaShape_NormalizedMoment_0_0_cyto", "AreaShape_NormalizedMoment_0_1_cyto",
"AreaShape_NormalizedMoment_1_0_cyto",
"Location",
"Orientation",
"AreaShape_Center_.",
"AreaShape_BoundingBoxMaximum_",
"AreaShape_BoundingBoxMinimum_",
"AreaShape_EulerNumber_",
#"FileName",
'Number_Object_Number_nuc', 
'PathName', 
'Parent'
  )
```

## Load data for each plate
```{r, echo=FALSE}
# Plate 1 - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P1_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P1/P1_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 2  - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P2_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P2/P2_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 3 - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT left, Cis Right
P3_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P3/P3_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 4 - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P4_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P4/P4_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")


# Plate 5  - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT Right, Cis Left ============================================================================================== ##
P5_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P5/P5_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 6 - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT Right, Cis Left ============================================================================================== ##
P6_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P6/P6_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 7 - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT right, Cis left ============================================================================================== ##
P7_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P7/P7_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 8 - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT right, Cis left ============================================================================================== ##
P8_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P8/P8_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 9  - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P9_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P9/P9_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 10 - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P10_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P10/P10_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 11  - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P11_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P11/P11_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

# Plate 12  - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT left, Cis Right ============================================================================================== ##
P12_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P12/P12_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

```

## Put meta data in and remove features

```{r, echo=FALSE}

## Doses for each treatment
# P1, 5, 9
cisDose <- c( "500", "2000", "5000", "10000", "20000", "40000", "80000")
dinaDose <- c("1.25", "2.5", "5", "10", "20", "40", "80")
doxoDose <- c("6.25", "12.5", "25", "50", "100", "200", "400")

# P2, 6, 10
flavoDose <- c("250", "500", "1000", "2000", "4000", "8000", "16000")
panoDose <- c("2.5", "5", "10", "20", "40", "80", "160")
sahaDose <- c("625", "1250", "2500", "5000", "10000", "20000", "40000")

# P3, 7, 11
gsk343Dose <- c("1562", "3125", "6250", "12500", "25000", "50000", "100000")
gsk467Dose <- c("625", "1250", "5000", "10000", "20000", "40000", "80000")
gsk503Dose <- c("1562.5", "3125", "6250", "12500", "50000", "100000")

# P4, P8, 12
gskJ4Dose <- c("312.5", "625", "1250", "2500", "5000", "10000", "20000")
iBET151Dose <- c("312.5", "625", "1250", "2500", "5000", "10000", "20000")
iBET726Dose <- c("4.12", "12.35", "37.04", "111.11", "333.33", "1000", "3000")

# Plate 1 - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P1_WT_NucLocs <- nucLoc(P1_WT)
P1_WT <- rmColumns(P1_WT, NACols)
P1_WT <- cpMakeMeta("P1", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("6.25", "12.5", "25", "50", "100", "200", "400"), c("6.25", "12.5", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P1_WT, 
                 "WT", 1:6, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"))


# Plate 2  - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P2_WT_NucLocs <- nucLoc(P2_WT)
P2_WT <- rmColumns(P2_WT, NACols)
P2_WT <- cpMakeMeta("P2", list(flavoDose, flavoDose, panoDose, panoDose, sahaDose, sahaDose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P2_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("Flavopiradol", "Flavopiradol", "Panobinostat", "Panobinostat", "SAHA", "SAHA") # treatments
                    )

# Plate 3 - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P3_WT_NucLocs <- nucLoc(P3_WT)
P3_WT <- rmColumns(P3_WT, NACols)
P3_WT <- cpMakeMeta("P3", list(gsk343Dose, gsk343Dose, gsk467Dose, gsk467Dose, gsk503Dose, gsk503Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P3_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("GSK343", "GSK343", "GSK467", "GSK467", "GSK503", "GSK503") # treatments
                    )

# Plate 4 - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P4_WT_NucLocs <- nucLoc(P4_WT)
P4_WT <- rmColumns(P4_WT, NACols)
P4_WT <- cpMakeMeta("P4", list(gskJ4Dose, gskJ4Dose, iBET151Dose, iBET151Dose, iBET726Dose, iBET726Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P4_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("GSKJ4", "GSKJ4", "iBET151", "iBET151", "iBET726", "iBET726") # treatments
                    )

# Plate 5  - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT Right, Cis Left ========================================================================================== ##
P5_WT_NucLocs <- nucLoc(P5_WT)
P5_WT <- rmColumns(P5_WT, NACols)

P5_WT <- cpMakeMeta("P1", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("6.25", "12.5", "25", "50", "100", "200", "400"), c("6.25", "12.5", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P5_WT, 
                 "WT", 7:12, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"))

# Plate 6 - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT Right, Cis Left ========================================================================================== ##
P6_WT_NucLocs <- nucLoc(P6_WT)
P6_WT <- rmColumns(P6_WT, NACols)
P6_WT <- cpMakeMeta("P6", list(flavoDose, flavoDose, panoDose, panoDose, sahaDose, sahaDose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P6_WT, # Plate Data set
                        "WT", 7:12, # cell line, plate columns
                        c("Flavopiradol", "Flavopiradol", "Panobinostat", "Panobinostat", "SAHA", "SAHA") # treatments
                    )

# Plate 7 - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT right, Cis left ========================================================================================== ##
P7_WT_NucLocs <- nucLoc(P7_WT)
P7_WT <- rmColumns(P7_WT, NACols)
P7_WT <- cpMakeMeta("P7", list(gsk343Dose, gsk343Dose, gsk467Dose, gsk467Dose, gsk503Dose, gsk503Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P7_WT, # Plate Data set
                        "WT", 7:12, # cell line, plate columns
                        c("GSK343", "GSK343", "GSK467", "GSK467", "GSK503", "GSK503") # treatments
                    )

# Plate 8 - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT right, Cis left ========================================================================================== ##
P8_WT_NucLocs <- nucLoc(P8_WT)
P8_WT <- rmColumns(P8_WT, NACols)
P8_WT <- cpMakeMeta("P8", list(gskJ4Dose, gskJ4Dose, iBET151Dose, iBET151Dose, iBET726Dose, iBET726Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P8_WT, # Plate Data set
                        "WT", 7:12, # cell line, plate columns
                        c("GSKJ4", "GSKJ4", "iBET151", "iBET151", "iBET726", "iBET726") # treatments
                    )

# Plate 9  - Cisplatin 1-2 (7-8), Dinaciclib 3-4 (9-10), Doxorubicin 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P9_WT_NucLocs <- nucLoc(P9_WT)
P9_WT <- rmColumns(P9_WT, NACols)

P9_WT <- cpMakeMeta("P1", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("6.25", "12.5", "25", "50", "100", "200", "400"), c("6.25", "12.5", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P9_WT, 
                 "WT", 1:6, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"))

# Plate 10 - Flavopiradol 1-2 (7-8), Panobinostat 3-4 (9-10), SAHA 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P10_WT_NucLocs <- nucLoc(P10_WT)
P10_WT <- rmColumns(P10_WT, NACols)
P10_WT <- cpMakeMeta("P10", list(flavoDose, flavoDose, panoDose, panoDose, sahaDose, sahaDose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P10_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("Flavopiradol", "Flavopiradol", "Panobinostat", "Panobinostat", "SAHA", "SAHA") # treatments
                    )

# Plate 11  - GSK343 1-2 (7-8), GSK467 3-4 (9-10), GSK503 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P11_WT_NucLocs <- nucLoc(P11_WT)
P11_WT <- rmColumns(P11_WT, NACols)
P11_WT <- cpMakeMeta("P11", list(gsk343Dose, gsk343Dose, gsk467Dose, gsk467Dose, gsk503Dose, gsk503Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P11_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("GSK343", "GSK343", "GSK467", "GSK467", "GSK503", "GSK503") # treatments
                    )


# Plate 12  - GSK-J4 1-2 (7-8), iBET 151 3-4 (9-10), GSK 503 5-6 (11-12) WT left, Cis Right ========================================================================================== ##
P12_WT_NucLocs <- nucLoc(P12_WT)
P12_WT <- rmColumns(P12_WT, NACols)
P12_WT <- cpMakeMeta("P12", list(gskJ4Dose, gskJ4Dose, iBET151Dose, iBET151Dose, iBET726Dose, iBET726Dose), # Doses
                        c("A", "A", "E", "E","F", "F"), # Untreated
                        P12_WT, # Plate Data set
                        "WT", 1:6, # cell line, plate columns
                        c("GSKJ4", "GSKJ4", "iBET151", "iBET151", "iBET726", "iBET726") # treatments
                    )

## metCols

metCols <- colnames(P1_WT)[1:11]
```
## Remove bad cells
```{r}


```

## normalisation
```{r}
dataCols <- colnames(P1_WT)[!(colnames(P1_WT) %in% metCols)]

## Scale Median, MAD function
scaleMedMad <- function(x, colNm = "untreated"){(x - median(x[x[, "Treatment"] == colNm,]))/mad(x[x[, "Treatment"] == colNm,])}

## Median of data
## R1
P1_WT_MED_UT <- (P1_WT[P1_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P2_WT_MED_UT <- (P2_WT[P2_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P3_WT_MED_UT <- (P3_WT[P3_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P4_WT_MED_UT <- (P4_WT[P4_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]

## R2
P5_WT_MED_UT <- (P5_WT[P5_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P6_WT_MED_UT <- (P6_WT[P6_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P7_WT_MED_UT <- (P7_WT[P7_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P8_WT_MED_UT <- (P8_WT[P8_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]

## R3
P9_WT_MED_UT <- (P9_WT[P9_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P10_WT_MED_UT <- (P10_WT[P10_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P11_WT_MED_UT <- (P11_WT[P11_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]
P12_WT_MED_UT <- (P12_WT[P12_WT$Treatment == "untreated",] %>% mutate_at(dataCols, median))[1,]

## MAD of data
## R1
P1_WT_MAD_UT <- (P1_WT[P1_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P2_WT_MAD_UT <- (P2_WT[P2_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P3_WT_MAD_UT <- (P3_WT[P3_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P4_WT_MAD_UT <- (P4_WT[P4_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]

## R2
P5_WT_MAD_UT <- (P5_WT[P5_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P6_WT_MAD_UT <- (P6_WT[P6_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P7_WT_MAD_UT <- (P7_WT[P7_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P8_WT_MAD_UT <- (P8_WT[P8_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]

## R3
P9_WT_MAD_UT <- (P9_WT[P9_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P10_WT_MAD_UT <- (P10_WT[P10_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P11_WT_MAD_UT <- (P11_WT[P11_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]
P12_WT_MAD_UT <- (P12_WT[P12_WT$Treatment == "untreated",] %>% mutate_at(dataCols, mad))[1,]


## Scaled Data

sclDtByMedMAD <- function(dt, medValues, madValues, datCols){
  ## dt should be a dataframe or tibble
  ## medValues should be a dataframe with 1 row and the same number of columns as dt with some median values of the columns
  ## madValues should be a dataframe with 1 row and the same number of columns as dt with some MAD values of the columns
  ## datCols should be a list of the metadata columns that we want to use
  #browser()
  dt[, datCols] <- sweep(dt[,datCols], 2, unlist(medValues[,datCols]),"-")
  dt[, datCols] <- sweep(dt[,datCols], 2, unlist(madValues[,datCols]),"/")
  
  return(dt)
}

## R1 ====================================================================================================================== ##
P1_WT_Nrm <- sclDtByMedMAD(P1_WT, P1_WT_MED_UT, P1_WT_MAD_UT, dataCols)
P2_WT_Nrm <- sclDtByMedMAD(P2_WT, P2_WT_MED_UT, P2_WT_MAD_UT, dataCols)
P3_WT_Nrm <- sclDtByMedMAD(P3_WT, P3_WT_MED_UT, P3_WT_MAD_UT, dataCols)
P4_WT_Nrm <- sclDtByMedMAD(P4_WT, P4_WT_MED_UT, P4_WT_MAD_UT, dataCols)
# 
# ## R2 ====================================================================================================================== ##
P5_WT_Nrm <- sclDtByMedMAD(P5_WT, P5_WT_MED_UT, P5_WT_MAD_UT, dataCols)
P6_WT_Nrm <- sclDtByMedMAD(P6_WT, P6_WT_MED_UT, P6_WT_MAD_UT, dataCols)
P7_WT_Nrm <- sclDtByMedMAD(P7_WT, P7_WT_MED_UT, P7_WT_MAD_UT, dataCols)
P8_WT_Nrm <- sclDtByMedMAD(P8_WT, P8_WT_MED_UT, P8_WT_MAD_UT, dataCols)
# ## R3 ====================================================================================================================== ##
P9_WT_Nrm <- sclDtByMedMAD(P9_WT, P9_WT_MED_UT, P9_WT_MAD_UT, dataCols)
P10_WT_Nrm <- sclDtByMedMAD(P10_WT, P10_WT_MED_UT, P10_WT_MAD_UT, dataCols)
P11_WT_Nrm <- sclDtByMedMAD(P11_WT, P11_WT_MED_UT, P11_WT_MAD_UT, dataCols)
P12_WT_Nrm <- sclDtByMedMAD(P12_WT, P12_WT_MED_UT, P12_WT_MAD_UT, dataCols)

rm(P1_WT)
rm(P2_WT)
rm(P3_WT)
rm(P4_WT)

rm(P5_WT)
rm(P6_WT)
rm(P7_WT)
rm(P8_WT)

rm(P9_WT)
rm(P10_WT)
rm(P11_WT)
rm(P12_WT)

gc()
```

## Remove single value and zero variance and NA values

```{r, remove NA columns}
## R1
P1_WT_Nrm_NACols <- listNaCols(P1_WT_Nrm, dataCols)
P2_WT_Nrm_NACols <- listNaCols(P2_WT_Nrm, dataCols)
P3_WT_Nrm_NACols <- listNaCols(P3_WT_Nrm, dataCols)
P4_WT_Nrm_NACols <- listNaCols(P4_WT_Nrm, dataCols)
## R2
P5_WT_Nrm_NACols <- listNaCols(P5_WT_Nrm, dataCols)
P6_WT_Nrm_NACols <- listNaCols(P6_WT_Nrm, dataCols)
P7_WT_Nrm_NACols <- listNaCols(P7_WT_Nrm, dataCols)
P8_WT_Nrm_NACols <- listNaCols(P8_WT_Nrm, dataCols)

##R3
P9_WT_Nrm_NACols <- listNaCols(P9_WT_Nrm, dataCols)
P10_WT_Nrm_NACols <- listNaCols(P10_WT_Nrm, dataCols)
P11_WT_Nrm_NACols <- listNaCols(P11_WT_Nrm, dataCols)
P12_WT_Nrm_NACols <- listNaCols(P12_WT_Nrm, dataCols)

AllNACols <- unique(c(P1_WT_Nrm_NACols, P2_WT_Nrm_NACols, P3_WT_Nrm_NACols, P4_WT_Nrm_NACols,
                   P5_WT_Nrm_NACols, P6_WT_Nrm_NACols, P7_WT_Nrm_NACols, P8_WT_Nrm_NACols,
                   P9_WT_Nrm_NACols, P10_WT_Nrm_NACols, P11_WT_Nrm_NACols, P12_WT_Nrm_NACols))

## Remove NA columns from all dataframes
dataCols <- dataCols[!(dataCols %in% AllNACols)]

# # R1
# P1_WT_Nrm <- P1_WT_Nrm[, c(metCols, dataCols)]
# P2_WT_Nrm <- P2_WT_Nrm[, c(metCols, dataCols)]
# P3_WT_Nrm <- P3_WT_Nrm[, c(metCols, dataCols)]
# P4_WT_Nrm <- P4_WT_Nrm[, c(metCols, dataCols)]
# 
# # R2
# P5_WT_Nrm <- P5_WT_Nrm[, c(metCols, dataCols)]
# P6_WT_Nrm <- P6_WT_Nrm[, c(metCols, dataCols)]
# P7_WT_Nrm <- P7_WT_Nrm[, c(metCols, dataCols)]
# P8_WT_Nrm <- P8_WT_Nrm[, c(metCols, dataCols)]
# 
# # R3
# P9_WT_Nrm <- P9_WT_Nrm[, c(metCols, dataCols)]
# P10_WT_Nrm <- P10_WT_Nrm[, c(metCols, dataCols)]
# P11_WT_Nrm <- P11_WT_Nrm[, c(metCols, dataCols)]
# P12_WT_Nrm <- P12_WT_Nrm[, c(metCols, dataCols)]
```

```{r, remove single value columns}
# R1
P1_WT_Nrm_SVCols <- listSingleValueCols(P1_WT_Nrm, dataCols)
P2_WT_Nrm_SVCols <- listSingleValueCols(P2_WT_Nrm, dataCols)
P3_WT_Nrm_SVCols <- listSingleValueCols(P3_WT_Nrm, dataCols)
P4_WT_Nrm_SVCols <- listSingleValueCols(P4_WT_Nrm, dataCols)

# R2
P5_WT_Nrm_SVCols <- listSingleValueCols(P5_WT_Nrm, dataCols)
P6_WT_Nrm_SVCols <- listSingleValueCols(P6_WT_Nrm, dataCols)
P7_WT_Nrm_SVCols <- listSingleValueCols(P7_WT_Nrm, dataCols)
P8_WT_Nrm_SVCols <- listSingleValueCols(P8_WT_Nrm, dataCols)

# R3
P9_WT_Nrm_SVCols <- listSingleValueCols(P9_WT_Nrm, dataCols)
P10_WT_Nrm_SVCols <- listSingleValueCols(P10_WT_Nrm, dataCols)
P11_WT_Nrm_SVCols <- listSingleValueCols(P11_WT_Nrm, dataCols)
P12_WT_Nrm_SVCols <- listSingleValueCols(P12_WT_Nrm, dataCols)

AllSVCols <- unique(c(P1_WT_Nrm_SVCols, P2_WT_Nrm_SVCols, P3_WT_Nrm_SVCols, P4_WT_Nrm_SVCols,
                   P5_WT_Nrm_SVCols, P6_WT_Nrm_SVCols, P7_WT_Nrm_SVCols, P8_WT_Nrm_SVCols,
                   P9_WT_Nrm_SVCols, P10_WT_Nrm_SVCols, P11_WT_Nrm_SVCols, P12_WT_Nrm_SVCols))

## Remove SV columns from all dataframes
dataCols <- dataCols[!(dataCols %in% AllSVCols)]

```

```{r, low variance columns}
# R1 doesn't seem to be a problem so leave
#P1_WT_Nrm_NZVarCols <- listNearZeroVar(P1_WT, dataCols)


```
## Get the median values of each well and each plate
```{r}
## Need the meta columns that are the same for each well for grouping

# R1
P1_WT_Well_Med <- getWellMed(P1_WT_Nrm, dataCols, metCols[c(4:6, 8:11)])
P2_WT_Well_Med <- getWellMed(P2_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P3_WT_Well_Med <- getWellMed(P3_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P4_WT_Well_Med <- getWellMed(P4_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 

# R2
P5_WT_Well_Med <- getWellMed(P5_WT_Nrm, dataCols, metCols[c(4:6, 8:11)])
P6_WT_Well_Med <- getWellMed(P6_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P7_WT_Well_Med <- getWellMed(P7_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P8_WT_Well_Med <- getWellMed(P8_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 

# R3
P9_WT_Well_Med <- getWellMed(P9_WT_Nrm, dataCols, metCols[c(4:6, 8:11)])
P10_WT_Well_Med <- getWellMed(P10_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P11_WT_Well_Med <- getWellMed(P11_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 
P12_WT_Well_Med <- getWellMed(P12_WT_Nrm, dataCols, metCols[c(4:6, 8:11)]) 

PAll_WT_Well_med <- rbind(P1_WT_Well_Med, P2_WT_Well_Med, P3_WT_Well_Med, P4_WT_Well_Med,
                          P5_WT_Well_Med, P6_WT_Well_Med, P7_WT_Well_Med, P8_WT_Well_Med,
                          P9_WT_Well_Med, P10_WT_Well_Med, P11_WT_Well_Med, P12_WT_Well_Med
                          )
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Remove correlated features
```{r}

PAll_Correlated_features <- findCorrelatedFeatures(PAll_WT_Well_med, dataCols)
dataColsNoCorr <- names(PAll_Correlated_features)
```

## PCA WT
```{r}

xx <- grepl("untreated|Cisplatin", PAll_WT_Well_med$Treatment)

pcaWT <- prcomp((PAll_WT_Well_med[, dataColsNoCorr]), scale = T)

pcaWTDf <- cbind(PAll_WT_Well_med[,metCols[c(4:6, 8:11)] ], data.frame(PC1 = pcaWT$x[,1], PC2 = pcaWT$x[,2], PC3 = pcaWT$x[,3]))
varExplained <- 100*pcaWT$sdev^2/sum(pcaWT$sdev^2)

ggplot(pcaWTDf, aes(x = PC1, y = PC2,  color = Treatment)) + 
  geom_point(size= 2) + xlab(paste("PC1: % Variance Explained = ", round(varExplained[1], 2))) + theme_bw() +
                               ylab(paste("PC2: % Variance Explained = ", round(varExplained[2], 1))) #+  xlim(-45, -30) + ylim(0, 10)
                               #xlim(-15, -5) + ylim(-5, 5)

ggplot(pcaWTDf, aes(x = PC1, y = PC3,  color = Treatment)) + 
  geom_point(size= 2) + xlab(paste("PC1: % Variance Explained = ", round(varExplained[1], 2))) + theme_bw() +
                               ylab(paste("PC3: % Variance Explained = ", round(varExplained[3], 1))) #+  xlim(-45, -30) + ylim(0, 10)

ggplot(pcaWTDf, aes(x = PC2, y = PC3,  color = Treatment)) + 
  geom_point(size= 2) + xlab(paste("PC2: % Variance Explained = ", round(varExplained[2], 2))) + theme_bw() +
                               ylab(paste("PC3: % Variance Explained = ", round(varExplained[3], 1))) #+  xlim(-45, -30) + ylim(0, 10)


```

## Theta Mapping

## Cell Cycle
```{r}

WT_Cisplatin_CellCycle <- P1_WT[grepl("untreated|Cisplatin",P1_WT$Treatment),c(metCols, "Intensity_IntegratedIntensity_DNA_Corr_nuc")]

for (dx in unique(WT_Cisplatin_CellCycle$Dose)){
  
  p <- ggplot(WT_Cisplatin_CellCycle[WT_Cisplatin_CellCycle$Dose == dx,], aes(x = Intensity_IntegratedIntensity_DNA_Corr_nuc)) + 
    geom_histogram(bins = 200, fill = "blue") + ggtitle(paste("Cell Cycle Cisplatin, Dose = ", dx)) + ylab("Count") + xlab("Integrated Intensity") +
    xlim(0, 30)
  ggsave(paste0("/data/DaveJames/Papers/CellPaintDose/FiguresMeeting141222/CellCycleDose_", dx, ".png") , p)
  
}
```