---
title: "Cisplatin_Paclitaxel_Subpopulations"
author: "David James"
date: "14/08/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(data.table)
library(ggplot2)
library(reshape2)
library(caret)
library(kohonen)
library(igraph)
library(pheatmap)
library(patchwork)
source("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/RScripts_011122/cellPaintFunctions.r")
source("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/RScripts_011122/cellPaintUnsupervisedFunctions.r")
```
## RLoad datasets

```{r features to remove}
# Features to remove (because of NA columns or location parameters)

NACols <- c("AreaShape_NormalizedMoment_0_0_nuc", "AreaShape_NormalizedMoment_0_1_nuc",  "AreaShape_NormalizedMoment_1_0_nuc",  "AreaShape_NormalizedMoment_0_0_cell",
 "AreaShape_NormalizedMoment_0_1_cell", "AreaShape_NormalizedMoment_1_0_cell", "AreaShape_NormalizedMoment_0_0_cyto", "AreaShape_NormalizedMoment_0_1_cyto",
"AreaShape_NormalizedMoment_1_0_cyto",
"Location",
"Orientation",
"AreaShape_Center_.",
"AreaShape_BoundingBoxMaximum_",
"AreaShape_BoundingBoxMinimum_",
"AreaShape_EulerNumber_",
#"FileName",
'Number_Object_Number_nuc', 
'Parent',
'PathName_Mito'
  )

```

## Load datasets

```{r, echo=FALSE, message=FALSE}

# Plate 1 WT
P1_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P1/P1_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")
P1_WT_NucLocs <- nucLoc(P1_WT)
P1_WT <- rmColumns(P1_WT, NACols)
P1_WT <- cpMakeMeta("P1", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P1_WT, 
                 "WT", 1:6, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"),
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P1 Drugs 1to3 R1_2022.05.17.15.06.00/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P1/P1_SegmentationImages/")

# Plate 1 cis
P1_Cis <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/RBGO_Storage/ResultsCisP01to04_09to12/P1/P1_Results/", 
                     prefix = "Cis_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

P1_Cis_NucLocs <- nucLoc(P1_Cis)
P1_Cis <- rmColumns(P1_Cis, NACols)

P1_Cis <- cpMakeMeta("P1", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P1_Cis, 
                 "Cis", 7:12, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"),
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P1 Drugs 1to3 R1_2022.05.17.15.06.00/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/RBGO_Storage/ResultsCisP01to04_09to12/P1/P1_SegmentationImages/")

# Plate 5 WT
P5_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P5/P5_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

P5_WT_NucLocs <- nucLoc(P5_WT)
P5_WT <- rmColumns(P5_WT, NACols)

P5_WT <- cpMakeMeta("P5", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P5_WT, 
                 "WT", 7:12, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"),
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P5 Drugs 1to3 R2_2022.05.18.13.05.25/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P5/P5_SegmentationImages/")

# Plate 5 Cis
P5_Cis <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P5/P5_Results/", 
                     prefix = "Cis_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

P5_Cis_NucLocs <- nucLoc(P5_Cis)
P5_Cis <- rmColumns(P5_Cis, NACols)

P5_Cis <- cpMakeMeta("P5", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P5_Cis, 
                 "Cis", 1:6, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"), 
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P5 Drugs 1to3 R2_2022.05.18.13.05.25/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P5/P5_SegmentationImages/")

# Plate 9 WT
P9_WT <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/headlessTest/P9/P9_Results/", 
                     prefix = "WT_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

P9_WT_NucLocs <- nucLoc(P9_WT)
P9_WT <- rmColumns(P9_WT, NACols)

P9_WT <- cpMakeMeta("P9", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P9_WT, 
                 "WT", 1:6, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"), 
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P9 Drugs 1to3 R3_2022.05.19.09.00.29/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/P9/P9_SegmentationImages/")

# Plate 9 Cis
P9_Cis <- load_CP_csv("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/RBGO_Storage/ResultsCisP01to04_09to12/P9/P9_Results/", 
                     prefix = "Cis_", nucSuf = "FilteredNuclei", cellSuf = "Cell", cytoSuf = "Cytoplasm")

P9_Cis_NucLocs <- nucLoc(P9_Cis)
P9_Cis <- rmColumns(P9_Cis, NACols)

P9_Cis <- cpMakeMeta("P9", list(c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), c( "500", "2000", "5000", "10000", "20000", "40000", "80000"), 
                              c("1.25", "2.5", "5", "10", "20", "40", "80"), c("1.25", "2.5", "5", "10", "20", "40", "80"),
                              c("12.5","6.25", "25", "50", "100", "200", "400"), c("12.5","6.25", "25", "50", "100", "200", "400")), 
                 c("A", "A", "E", "E","F", "F"), P9_Cis, 
                 "Cis", 7:12, 
                 c("Cisplatin", "Cisplatin", "Dinaciclib", "Dinaciclib", "Doxorubicin", "Doxorubicin"),
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/Cell Paint Ibidi 10x/Cell Paint Ibidi 10x_P9 Drugs 1to3 R3_2022.05.19.09.00.29/",
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/CellProfilerOutputs/RBGO_Storage/ResultsCisP01to04_09to12/P9/P9_SegmentationImages/")

metCols <- colnames(P1_WT)[1:14]
datCols <- colnames(P1_WT)[15:length(colnames(P1_WT))]

```
## Make DF of all cisplation and Dox treatments and untreated samples (note that I have not added Dox to sample labels, need to do this for consistency!)
```{r}

WT_CisplatinUntreated <- rbind(P1_WT[grepl("untreated|Cisplatin|Doxorubicin", P1_WT$Treatment), ],
                               P5_WT[grepl("untreated|Cisplatin|Doxorubicin", P5_WT$Treatment), ],
                               P9_WT[grepl("untreated|Cisplatin|Doxorubicin", P9_WT$Treatment), ])

# write.csv(WT_CisplatinUntreated, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/WT_Raw_Data.csv")

WT_CisplatinUntreated_nucLocs <- rbind(P1_WT_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P1_WT$Treatment), ],
                               P5_WT_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P5_WT$Treatment), ],
                               P9_WT_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P9_WT$Treatment), ]) 


Cis_CisplatinUntreated <- rbind(P1_Cis[grepl("untreated|Cisplatin|Doxorubicin", P1_Cis$Treatment), ],
                                P5_Cis[grepl("untreated|Cisplatin|Doxorubicin", P5_Cis$Treatment), ],
                                P9_Cis[grepl("untreated|Cisplatin|Doxorubicin", P9_Cis$Treatment), ])

# write.csv(Cis_CisplatinUntreated, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/Cis_Raw_Data.csv")

Cis_CisplatinUntreated_nucLocs <- rbind(P1_Cis_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P1_Cis$Treatment), ],
                                P5_Cis_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P5_Cis$Treatment), ],
                                P9_Cis_NucLocs[grepl("untreated|Cisplatin|Doxorubicin", P9_Cis$Treatment), ])

```

## Perform standard analysis of cell paint to get a limited set of parameters
Order of operations:
  1) Get the median and MAD of all parameters for UT by well and by plate
  2) Check that the levels are the same across the plates
  
```{r, Normalization of plates and wells}



# Median values
WT_Med_Untreated <- WT_CisplatinUntreated %>% filter(Treatment == "untreated") %>% select(c("plate", "Metadata_Well_nuc",  datCols)) %>% group_by(Metadata_Well_nuc, plate) %>%  
                      summarise_at(datCols, median, na.rm = TRUE)

Cis_Med_Untreated <- Cis_CisplatinUntreated %>% filter(Treatment == "untreated") %>% select(c("plate", "Metadata_Well_nuc",  datCols)) %>% group_by(Metadata_Well_nuc, plate) %>%  
                      summarise_at(datCols, median, na.rm = TRUE)


WT_Med_Untreated_AllWells <- WT_CisplatinUntreated %>% filter(Treatment == "untreated") %>% summarise_at(datCols, median, na.rm = TRUE) #apply(WT_Med_Untreated[, datCols], 2,median)
Cis_Med_Untreated_AllWells <- Cis_CisplatinUntreated %>% filter(Treatment == "untreated") %>% summarise_at(datCols, median, na.rm = TRUE) #apply(Cis_Med_Untreated[, datCols], 2,median)

# MAD values
WT_MAD_Untreated <- WT_CisplatinUntreated %>% filter(Treatment == "untreated") %>% select(c("plate", "Metadata_Well_nuc",  datCols)) %>% group_by(Metadata_Well_nuc, plate) %>%  
                      summarise_at(datCols, mad, na.rm = TRUE)

Cis_MAD_Untreated <- Cis_CisplatinUntreated %>% filter(Treatment == "untreated") %>% select(c("plate", "Metadata_Well_nuc",  datCols)) %>% group_by(Metadata_Well_nuc, plate) %>%  
                      summarise_at(datCols, mad, na.rm = TRUE)

WT_MAD_Untreated_AllWells <- WT_CisplatinUntreated %>% filter(Treatment == "untreated") %>% summarise_at(datCols, mad, na.rm = TRUE) #apply(WT_Med_Untreated[, datCols], 2,median)
Cis_MAD_Untreated_AllWells <- Cis_CisplatinUntreated %>% filter(Treatment == "untreated") %>% summarise_at(datCols, mad, na.rm = TRUE)#apply(Cis_Med_Untreated[, datCols], 2,mad)

## Channels

## Measurement modules
channels <- c("DNA_Corr", "CytoSkelCorr", "ER_Corr", "Mitochondria_Corr")
areas <- c("nuc", "cell", "cyto")
#measureModules <- c("AreaShape", "Correlation", "Granularity", "Intensity", "Radial", "Texture")
measureModules <- c("Correlation", "Granularity", "Intensity", "Radial", "Texture")

## Plot heatmap of results

absWTMadGrt_All <- data.frame(Grt1 = NULL, Grt1p5 = NULL, Grt2 = NULL)
absCisMadGrt_All <- data.frame(Grt1 = NULL, Grt1p5 = NULL, Grt2 = NULL)
# loop through areas
for (ax in areas){
  # loop through modules
  for(mx in measureModules){
    for(cx in channels){
    
      ##WT ============================================================================================================================== ##
      
    tDf <- data.frame(WT_Med_Untreated[,which(grepl(paste0("^",mx, ".*", cx, ".*",ax, sep = ""), colnames(WT_Med_Untreated)))])
    rownames(tDf) <- paste(WT_Med_Untreated$plate, WT_Med_Untreated$Metadata_Well_nuc, sep = "_")

    tDf <- sclDtByMedMAD(tDf, WT_Med_Untreated_AllWells, WT_MAD_Untreated_AllWells, colnames(tDf))
    
    tDf <- tDf[,!colSums(is.na(tDf))]
    
    x <- pheatmap(as.matrix((tDf)),  cluster_cols = F, cluster_rows = F, fontsize_row = 8, fontsize_col = 7, display_numbers = round(as.matrix(tDf), 2), fontsize = 4,
                  color = c("blue","green", "yellow", "orange", "red"), breaks = c(min(c(min(tDf), -2.5)), -2, -1, 1, 2, max(c(max(tDf), 2.5))))
    save_pheatmap_png(x, paste("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/Figures/WT_MAD_Div", mx, ax, cx, sep = "_"), width = 12*ncol(tDf) + 500, height = 800)
    
    # Summary of parameters outside MAD
    absWTMadGrt1 <- rowSums(abs(t(tDf)) > 1)
    absWTMadGrt1p5 <- rowSums(abs(t(tDf)) > 1.5)
    absWTMadGrt2 <- rowSums(abs(t(tDf)) > 2)
    
    absWTMadGrt <- data.frame(Grt1 = absWTMadGrt1, Grt1p5 = absWTMadGrt1p5, Grt2 = absWTMadGrt2)
    absWTMadGrt_All <- rbind(absWTMadGrt_All,absWTMadGrt)
    ## cis ============================================================================================================================== ##
    
    tDf <- data.frame(Cis_Med_Untreated[,which(grepl(paste0("^",mx, ".*", cx, ".*",ax, sep = ""), colnames(Cis_Med_Untreated)))])
    rownames(tDf) <- paste(Cis_Med_Untreated$plate, Cis_Med_Untreated$Metadata_Well_nuc, sep = "_")

    tDf <- sclDtByMedMAD(tDf, Cis_Med_Untreated_AllWells, Cis_MAD_Untreated_AllWells, colnames(tDf))
    
    tDf <- tDf[,!colSums(is.na(tDf))]
    
    x <- pheatmap(as.matrix((tDf)),  cluster_cols = F, cluster_rows = F, fontsize_row = 8, fontsize_col = 7, display_numbers = round(as.matrix(tDf), 2), fontsize = 4,
                  color = c("blue","green", "yellow", "orange", "red"), breaks = c(min(c(min(tDf), -2.5)), -2, -1, 1, 2, max(c(max(tDf), 2.5))))
    save_pheatmap_png(x, paste("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/Figures/Cis_MAD_Div", mx, ax, cx, sep = "_"), width = 14*ncol(tDf) + 500, height = 1000)  
    
    # Summary of parameters outside MAD
    absCisMadGrt1 <- rowSums(abs(t(tDf)) > 1)
    absCisMadGrt1p5 <- rowSums(abs(t(tDf)) > 1.5)
    absCisMadGrt2 <- rowSums(abs(t(tDf)) > 2)
    
    absCisMadGrt <- data.frame(Grt1 = absCisMadGrt1, Grt1p5 = absCisMadGrt1p5, Grt2 = absCisMadGrt2) 
    absCisMadGrt_All <- rbind(absCisMadGrt_All,absCisMadGrt)
  }
}
}

```

## Filter 'unstable' features 
```{r}
# Get rid of parameters with wells with median value > 1 MAD from all median values

MADFiltParameters <- unique(c(rownames(absWTMadGrt_All[absWTMadGrt_All$Grt1 > 0,]), rownames(absCisMadGrt_All[absCisMadGrt_All$Grt1 > 0,])))

## change datCols
datCols <- datCols[!(datCols %in% MADFiltParameters)]

# Remove columns from main datasets
WT_CisplatinUntreated <- WT_CisplatinUntreated[,c(metCols, datCols)]
Cis_CisplatinUntreated <- Cis_CisplatinUntreated[,c(metCols, datCols)]

```

## Create dataframe with both WT and Cis
```{r}

WT_Cis_CisplatinDoxUntreated <- rbind(WT_CisplatinUntreated, Cis_CisplatinUntreated)

```

## Normalize data
```{r}

## Get median and mad of untreared for each plate
#WT
WT_Med_Untreated_Plate <- WT_CisplatinUntreated %>% dplyr::filter(Treatment == "untreated") %>% dplyr::select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, median, na.rm = TRUE)
WT_MAD_Untreated_Plate <- WT_CisplatinUntreated %>% dplyr::filter(Treatment == "untreated") %>% dplyr::select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, mad, na.rm = TRUE)

WT_CisplatinUntreatedNrm <- data.frame()
for (dx in unique(WT_CisplatinUntreated$plate)){
  
  WT_CisplatinUntreatedNrm <- rbind(WT_CisplatinUntreatedNrm, 
                                    sclDtByMedMAD(WT_CisplatinUntreated[WT_CisplatinUntreated$plate == dx, ],
                                                  WT_Med_Untreated_Plate[WT_Med_Untreated_Plate$plate == dx, ], 
                                                  WT_MAD_Untreated_Plate[WT_MAD_Untreated_Plate$plate == dx, ],
                                                  datCols))
  
}

# Cis
Cis_Med_Untreated_Plate <- Cis_CisplatinUntreated %>% dplyr::filter(Treatment == "untreated") %>% dplyr::select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, median, na.rm = TRUE)
Cis_MAD_Untreated_Plate <- Cis_CisplatinUntreated %>% dplyr::filter(Treatment == "untreated") %>% dplyr::select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, mad, na.rm = TRUE)

Cis_CisplatinUntreatedNrm <- data.frame()
for (dx in unique(Cis_CisplatinUntreated$plate)){
  
  Cis_CisplatinUntreatedNrm <- rbind(Cis_CisplatinUntreatedNrm, 
                                    sclDtByMedMAD(Cis_CisplatinUntreated[Cis_CisplatinUntreated$plate == dx, ],
                                                  Cis_Med_Untreated_Plate[Cis_Med_Untreated_Plate$plate == dx, ], 
                                                  Cis_MAD_Untreated_Plate[Cis_MAD_Untreated_Plate$plate == dx, ],
                                                  datCols))
  
}

## Get median and mad of untreated for both plates together
# WT_Cis_Med_Untreated_Plate <- rbind(WT_CisplatinUntreated[WT_CisplatinUntreated$Treatment == "untreated",], Cis_CisplatinUntreated[Cis_CisplatinUntreated$Treatment == "untreated",]) %>% select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, median, na.rm = TRUE)
# WT_Cis_MAD_Untreated_Plate <- rbind(WT_CisplatinUntreated[WT_CisplatinUntreated$Treatment == "untreated",], Cis_CisplatinUntreated[Cis_CisplatinUntreated$Treatment == "untreated",]) %>% select(c("plate", datCols)) %>% group_by(plate) %>% summarise_at(datCols, mad, na.rm = TRUE)

# Just average the median and mads of the WT and Cis seperately

WT_Cis_Med_Untreated_Plate <- WT_Med_Untreated_Plate
WT_Cis_Med_Untreated_Plate[,2:ncol(WT_Cis_Med_Untreated_Plate)] <- (WT_Cis_Med_Untreated_Plate[,2:ncol(WT_Cis_Med_Untreated_Plate)] + Cis_Med_Untreated_Plate[,2:ncol(Cis_Med_Untreated_Plate)])/2

WT_Cis_MAD_Untreated_Plate <- WT_MAD_Untreated_Plate
WT_Cis_MAD_Untreated_Plate[,2:ncol(WT_Cis_MAD_Untreated_Plate)] <- (WT_Cis_MAD_Untreated_Plate[,2:ncol(WT_Cis_MAD_Untreated_Plate)] + Cis_MAD_Untreated_Plate[,2:ncol(Cis_MAD_Untreated_Plate)])/2

WT_Cis_CisplatinDoxUntreatedNrm <- data.frame()
for (dx in unique(WT_Cis_CisplatinDoxUntreated$plate)){
  
  WT_Cis_CisplatinDoxUntreatedNrm <- rbind(WT_Cis_CisplatinDoxUntreatedNrm, 
                                           sclDtByMedMAD(WT_Cis_CisplatinDoxUntreated[WT_Cis_CisplatinDoxUntreated$plate == dx,],
                                                         WT_Cis_Med_Untreated_Plate[WT_Cis_Med_Untreated_Plate$plate == dx,],
                                                         WT_Cis_MAD_Untreated_Plate[WT_Cis_MAD_Untreated_Plate$plate == dx, ],
                                                         datCols
                                                         ))
  
}

```

## Filter normed data
  1) Remove NA columns
  2) Remove 0 columns
  3) Remove low variance columns
```{r}
## Get NA columns
WT_NaCols <- listNaCols(WT_CisplatinUntreatedNrm, datCols)
Cis_NaCols <- listNaCols(Cis_CisplatinUntreatedNrm, datCols)

datCols <- datCols[!(datCols %in% unique(c(WT_NaCols, Cis_NaCols)))]
WT_CisplatinUntreatedNrm <- WT_CisplatinUntreatedNrm[, c(metCols, datCols)]
Cis_CisplatinUntreatedNrm <- Cis_CisplatinUntreatedNrm[, c(metCols, datCols)]
WT_Cis_CisplatinDoxUntreatedNrm <- WT_Cis_CisplatinDoxUntreatedNrm[, c(metCols, datCols)]

## Get single value columns
WT_SingleValueCols <- listSingleValueCols(WT_CisplatinUntreatedNrm, datCols)
Cis_SingleValueCols <- listSingleValueCols(Cis_CisplatinUntreatedNrm, datCols)

```

## The number of MAD away from the median
```{r}
MADs <- 10

WTMaxMAD_Dev <- getMaxMAD_Diff(WT_CisplatinUntreatedNrm, datCols)

WTMaxFeaturesGrt10 <- 100*colSums(WTMaxMAD_Dev > MADs)/nrow(WT_CisplatinUntreatedNrm) 
WTMaxFeaturesGrt10Rm <- names(WTMaxFeaturesGrt10[WTMaxFeaturesGrt10 > 1])
  
  
CisMaxMAD_Dev <- getMaxMAD_Diff(Cis_CisplatinUntreatedNrm, datCols)

CisMaxFeaturesGrt10 <- 100*colSums(CisMaxMAD_Dev > MADs)/nrow(Cis_CisplatinUntreatedNrm) 
CisMaxFeaturesGrt10Rm <- names(CisMaxFeaturesGrt10[CisMaxFeaturesGrt10 > 1])

## Remove the Max Deviation features
datCols <- datCols[!(datCols %in% unique(c(WTMaxFeaturesGrt10Rm, CisMaxFeaturesGrt10Rm)))]
WT_CisplatinUntreatedNrm <- WT_CisplatinUntreatedNrm[, c(metCols, datCols)]
Cis_CisplatinUntreatedNrm <- Cis_CisplatinUntreatedNrm[, c(metCols, datCols)]
WT_Cis_CisplatinDoxUntreatedNrm <- WT_Cis_CisplatinDoxUntreatedNrm[, c(metCols, datCols)]
```

## Correlations
```{r}
## Find correlated features
WT_Cis_CorrelatedFeatures_IndNrm <- findCorrelatedFeatures(rbind(WT_CisplatinUntreatedNrm, Cis_CisplatinUntreatedNrm), datCols, corThres = 0.9)
WT_Cis_CorrelatedFeatures_CmbNrm <- findCorrelatedFeatures(WT_Cis_CisplatinDoxUntreatedNrm, datCols, corThres = 0.9)

## Make dat column lists for the individually normalized and the combined normalized
datColsInd <- datCols[(datCols %in% WT_Cis_CorrelatedFeatures_IndNrm)]
datColsCmb <- datCols[(datCols %in% WT_Cis_CorrelatedFeatures_CmbNrm)]

## Set the main arrays to contain only the non-correlated features
WT_CisplatinUntreatedNrm <- WT_CisplatinUntreatedNrm[, c(metCols, datColsInd)]
Cis_CisplatinUntreatedNrm <- Cis_CisplatinUntreatedNrm[, c(metCols, datColsInd)]
WT_Cis_CisplatinDoxUntreatedNrm <- WT_Cis_CisplatinDoxUntreatedNrm[, c(metCols, datColsCmb)]

# WT_CorrelatedFeatures <- findCorrelatedFeatures(WT_CisplatinUntreatedNrm, datCols, corThres = 0.9)
# 
# Cis_CorrelatedFeatures <- findCorrelatedFeatures(Cis_CisplatinUntreatedNrm, datCols, corThres = 0.9)
# 
# WT_Cis_CorrelatedFeatures <- names(Cis_CorrelatedFeatures)[names(Cis_CorrelatedFeatures) %in% names(WT_CorrelatedFeatures)]
# 
# datCols <- datCols[(datCols %in% WT_Cis_CorrelatedFeatures)]
# WT_CisplatinUntreatedNrm <- WT_CisplatinUntreatedNrm[, c(metCols, datCols)]
# Cis_CisplatinUntreatedNrm <- Cis_CisplatinUntreatedNrm[, c(metCols, datCols)]
# WT_Cis_CisplatinDoxUntreatedNrm <- WT_Cis_CisplatinDoxUntreatedNrm[, c(metCols, datCols)]

#WT_Cis_Ind_CorrelatedFeatures <- findCorrelatedFeatures(datCols)

```

## Get the well medians
```{r}

WT_CisplatinUntreatedNrmMed <- WT_CisplatinUntreatedNrm %>% group_by(plate, Metadata_Well_nuc, Treatment, Dose, cell_line) %>% summarise_at(datColsInd, median)

Cis_CisplatinUntreatedNrmMed <- Cis_CisplatinUntreatedNrm %>% group_by(plate, Metadata_Well_nuc, Treatment, Dose, cell_line) %>% summarise_at(datColsInd, median)

WT_Cis_CisplatinDoxUntreatedNrmMed <- WT_Cis_CisplatinDoxUntreatedNrm %>% group_by(plate, Metadata_Well_nuc, Treatment, Dose, cell_line) %>% summarise_at(datColsCmb, median)

# Write normalized data to csv (cell level)
# write.csv(WT_CisplatinUntreatedNrm[!(WT_CisplatinUntreatedNrm$Treatment == "Doxorubicin"),], "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/NormalizedDataSets/WT_cells_WTNormed.csv")
# write.csv(Cis_CisplatinUntreatedNrm[!(Cis_CisplatinUntreatedNrm$Treatment == "Doxorubicin"),], "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/NormalizedDataSets/Cis_cells_WTNormed.csv")
# write.csv(WT_Cis_CisplatinUntreatedNrm[!(WT_Cis_CisplatinUntreatedNrm$Treatment == "Doxorubicin"),], "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/NormalizedDataSets/WTandCis_cells_WTandCisNormed.csv")

```

## Get doses as function of  LD50s
```{r}
## WT_Cis untreated dose
WT_CisplatinUntreatedNrmMed$Dose_IC50 <- 0
WT_CisplatinUntreatedNrmMed[WT_CisplatinUntreatedNrmMed$Treatment == "Cisplatin",]$Dose_IC50 <- log10(as.numeric(WT_CisplatinUntreatedNrmMed[WT_CisplatinUntreatedNrmMed$Treatment == "Cisplatin", ]$Dose))/(3.420)
WT_CisplatinUntreatedNrmMed[WT_CisplatinUntreatedNrmMed$Treatment == "Doxorubicin",]$Dose_IC50 <- log10(as.numeric(WT_CisplatinUntreatedNrmMed[WT_CisplatinUntreatedNrmMed$Treatment == "Doxorubicin", ]$Dose))/(0.851)

## Cis_CisplatinUntreatedNrmMed 
Cis_CisplatinUntreatedNrmMed$Dose_IC50 <- 0
Cis_CisplatinUntreatedNrmMed[Cis_CisplatinUntreatedNrmMed$Treatment == "Cisplatin",]$Dose_IC50 <- log10(as.numeric(Cis_CisplatinUntreatedNrmMed[Cis_CisplatinUntreatedNrmMed$Treatment == "Cisplatin", ]$Dose))/(5.164)
Cis_CisplatinUntreatedNrmMed[Cis_CisplatinUntreatedNrmMed$Treatment == "Doxorubicin",]$Dose_IC50 <- log10(as.numeric(Cis_CisplatinUntreatedNrmMed[Cis_CisplatinUntreatedNrmMed$Treatment == "Doxorubicin", ]$Dose))/(0.470)

## WT/Cis cisplatin untreated dose
WT_Cis_CisplatinDoxUntreatedNrmMed$Dose_IC50 <- 0

WT_Cis_Idx <- WT_Cis_CisplatinDoxUntreatedNrmMed$cell_line == "WT" & WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment == "Cisplatin"
Cis_Cis_Idx <- WT_Cis_CisplatinDoxUntreatedNrmMed$cell_line == "Cis" & WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment == "Cisplatin"
WT_Dox_Idx <- WT_Cis_CisplatinDoxUntreatedNrmMed$cell_line == "WT" & WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment == "Doxorubicin"
Cis_Dox_Idx <- WT_Cis_CisplatinDoxUntreatedNrmMed$cell_line == "Cis" & WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment == "Doxorubicin"

WT_Cis_CisplatinDoxUntreatedNrmMed$Dose_IC50[WT_Cis_Idx] <- log10(as.numeric(WT_Cis_CisplatinDoxUntreatedNrmMed$Dose))[WT_Cis_Idx]/3.420
WT_Cis_CisplatinDoxUntreatedNrmMed$Dose_IC50[Cis_Cis_Idx] <- log10(as.numeric(WT_Cis_CisplatinDoxUntreatedNrmMed$Dose))[Cis_Cis_Idx]/5.164
WT_Cis_CisplatinDoxUntreatedNrmMed$Dose_IC50[WT_Cis_Idx] <- log10(as.numeric(WT_Cis_CisplatinDoxUntreatedNrmMed$Dose))[WT_Dox_Idx]/0.851
WT_Cis_CisplatinDoxUntreatedNrmMed$Dose_IC50[Cis_Dox_Idx] <- log10(as.numeric(WT_Cis_CisplatinDoxUntreatedNrmMed$Dose))[Cis_Dox_Idx]/0.470

```


## PCA plots
```{r}
## WT
# WT_CisplatinUntreatedNrmMedPCA_IndividualNrm_IndividualNrm <- prcomp(as.matrix(WT_CisplatinUntreatedNrmMed[, datCols]))
# 
# WT_CisplatinUntreatedNrmMedPCA_IndividualNrmDf <- cbind(WT_CisplatinUntreatedNrmMed[,1:4], 
#                                           data.frame(PC1 = WT_CisplatinUntreatedNrmMedPCA_IndividualNrm$x[,1], 
#                                                      PC2 = WT_CisplatinUntreatedNrmMedPCA_IndividualNrm$x[,2], 
#                                                      PC3 = WT_CisplatinUntreatedNrmMedPCA_IndividualNrm$x[,3]))
# 
# WT_CisplatinUntreatedNrmMedPCA_IndividualNrmDf$Dose <- factor(as.numeric(WT_CisplatinUntreatedNrmMedPCA_IndividualNrmDf$Dose), levels = sort(unique(as.numeric(WT_CisplatinUntreatedNrmMedPCA_IndividualNrmDf$Dose))))
# 
# varExplained <- 100*WT_CisplatinUntreatedNrmMedPCA_IndividualNrm$sdev^2/sum(WT_CisplatinUntreatedNrmMedPCA_IndividualNrm$sdev^2)
# 
# ggplot(WT_CisplatinUntreatedNrmMedPCA_IndividualNrmDf, aes(x = PC1, y = PC2,  color = Dose, shape = Treatment)) + 
#     geom_point(size= 3) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() +
#                                ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT Dose response")


## WT and Cisplatin normed
WT_CisplatinUntreatedNrmMedPCA_CmbNrm <- prcomp(as.matrix(WT_Cis_CisplatinDoxUntreatedNrmMed[grepl('untreated|Cisplatin', WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment), datColsCmb]))

WT_CisplatinUntreatedNrmMedPCA_CmbNrmDf <- cbind(WT_Cis_CisplatinDoxUntreatedNrmMed[grepl('untreated|Cisplatin', WT_Cis_CisplatinDoxUntreatedNrmMed$Treatment),1:5], 
                                          data.frame(PC1 = WT_CisplatinUntreatedNrmMedPCA_CmbNrm$x[,1], 
                                                     PC2 = WT_CisplatinUntreatedNrmMedPCA_CmbNrm$x[,2], 
                                                     PC3 = WT_CisplatinUntreatedNrmMedPCA_CmbNrm$x[,3]))

WT_CisplatinUntreatedNrmMedPCA_CmbNrmDf$Dose <- factor(as.numeric(WT_CisplatinUntreatedNrmMedPCA_CmbNrmDf$Dose), levels = sort(unique(as.numeric(WT_CisplatinUntreatedNrmMedPCA_CmbNrmDf$Dose))))

varExplained <- 100*WT_CisplatinUntreatedNrmMedPCA_CmbNrm$sdev^2/sum(WT_CisplatinUntreatedNrmMedPCA_CmbNrm$sdev^2)

ggplot(WT_CisplatinUntreatedNrmMedPCA_CmbNrmDf, aes(x = PC1, y = PC2,  color = Dose, shape = cell_line, fill = cell_line)) + 
    geom_point(size= 3) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() + scale_fill_manual(values = c("blue", "red")) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT and Cis Normed Dose response")


## WT + Cis ========================================================================================== ##

WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm <- prcomp(as.matrix(rbind(WT_CisplatinUntreatedNrmMed[grepl("untreated|Cisplatin", WT_CisplatinUntreatedNrmMed$Treatment), datColsInd], Cis_CisplatinUntreatedNrmMed[grepl("untreated|Cisplatin", Cis_CisplatinUntreatedNrmMed$Treatment), datColsInd])))

WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrmDf <- cbind(rbind(WT_CisplatinUntreatedNrmMed[grepl("untreated|Cisplatin", WT_CisplatinUntreatedNrmMed$Treatment), 1:5], Cis_CisplatinUntreatedNrmMed[grepl("untreated|Cisplatin",Cis_CisplatinUntreatedNrmMed$Treatment),1:5]), 
                                          data.frame(PC1 = WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$x[,1], 
                                                     PC2 = WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$x[,2], 
                                                     PC3 = WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$x[,3]))

WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrmDf$Dose <- factor(as.numeric(WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrmDf$Dose), levels = sort(unique(as.numeric(WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrmDf$Dose))))

varExplained <- 100*WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$sdev^2/sum(WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$sdev^2)

ggplot(WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrmDf, aes(x = PC1, y = PC2,  color = Dose, shape = cell_line)) + 
    geom_point(size= 3) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%"))  + ggtitle("WT + Cis Indiviudally normed Dose response")


```
## Dimensionaltiy reduction of single cells
```{r, fig.width=15}
set.seed(432)
library(Rtsne)

## 
smpN <- 1000 # number of cells from each treatment/dose

## Combined normalization
WT_Cis_Cells_CmbNorm <- WT_Cis_CisplatinDoxUntreatedNrm[which(!grepl("Doxorubicin", WT_Cis_CisplatinDoxUntreatedNrm$Treatment)), ] %>% group_by(Dose, cell_line) %>% slice_sample(n = smpN)

WT_Cis_Cells_CmbNormPCA <- prcomp(as.matrix(WT_Cis_Cells_CmbNorm[, datColsCmb]))

WT_Cis_Cells_CmbNormPCADf <- cbind(WT_Cis_Cells_CmbNorm[,1:13], 
                                          data.frame(PC1 = WT_Cis_Cells_CmbNormPCA$x[,1], 
                                                     PC2 = WT_Cis_Cells_CmbNormPCA$x[,2], 
                                                     PC3 = WT_Cis_Cells_CmbNormPCA$x[,3]))

WT_Cis_Cells_CmbNormPCADf$Dose <- factor(as.numeric(WT_Cis_Cells_CmbNormPCADf$Dose), levels = sort(unique(as.numeric(WT_Cis_Cells_CmbNormPCADf$Dose))))

varExplained <- 100*WT_Cis_Cells_CmbNormPCA$sdev^2/sum(WT_Cis_Cells_CmbNormPCA$sdev^2)

ggplot(WT_Cis_Cells_CmbNormPCADf, aes(x = PC1, y = PC2,  color = Dose, shape = Treatment)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() +  xlim(-60, 110) + ylim(-100, 70) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT+Cis combined Normalization") + guides(colour = guide_legend(override.aes = list(size=10)))

ggplot(WT_Cis_Cells_CmbNormPCADf[WT_Cis_Cells_CmbNormPCADf$cell_line == "WT", ], aes(x = PC1, y = PC2,  color = Dose)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() + xlim(-60, 110) + ylim(-100, 70) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT WT+Cis combined Normalization") + guides(colour = guide_legend(override.aes = list(size=10)))

ggplot(WT_Cis_Cells_CmbNormPCADf[WT_Cis_Cells_CmbNormPCADf$cell_line == "Cis", ], aes(x = PC1, y = PC2,  color = Dose)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() + xlim(-60, 110) + ylim(-100, 70) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("Cis WT+Cis combined Normalization") + guides(colour = guide_legend(override.aes = list(size=10)))

## Separate normalization
WT_Cis_Cells_SepNorm <- rbind(WT_CisplatinUntreatedNrm[!grepl("Doxorubicin",WT_CisplatinUntreatedNrm$Treatment),], Cis_CisplatinUntreatedNrm[!grepl("Doxorubicin",Cis_CisplatinUntreatedNrm$Treatment),]) 

WT_Cis_Cells_SepNormSmp <- WT_Cis_Cells_SepNorm[which(!grepl("Doxorubicin", WT_Cis_Cells_SepNorm$Treatment)), ] %>% group_by(Dose, cell_line) %>% slice_sample(n = smpN)

WT_Cis_Cells_SepNormPCA <- prcomp(as.matrix(WT_Cis_Cells_SepNorm[, datColsInd]))

WT_Cis_Cells_SepNormPCADf <- cbind(WT_Cis_Cells_SepNorm[,1:13], 
                                          data.frame(PC1 = WT_Cis_Cells_SepNormPCA$x[,1], 
                                                     PC2 = WT_Cis_Cells_SepNormPCA$x[,2], 
                                                     PC3 = WT_Cis_Cells_SepNormPCA$x[,3]))

WT_Cis_Cells_SepNormPCADf$Dose <- factor(as.numeric(WT_Cis_Cells_SepNormPCADf$Dose), levels = sort(unique(as.numeric(WT_Cis_Cells_SepNormPCADf$Dose))))

varExplained <- 100*WT_Cis_Cells_SepNormPCA$sdev^2/sum(WT_Cis_Cells_SepNormPCA$sdev^2)

# rm outliers
WT_Cis_Cells_SepNormPCADf <- WT_Cis_Cells_SepNormPCADf[WT_Cis_Cells_SepNormPCADf$PC1 > -100,]

ggplot(WT_Cis_Cells_SepNormPCADf, aes(x = PC1, y = PC2,  color = Dose, shape = Treatment)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() + xlim(-100, 70) + ylim(-110, 100) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT Cis seperate Normalization") + guides(colour = guide_legend(override.aes = list(size=10)))


ggplot(WT_Cis_Cells_SepNormPCADf[WT_Cis_Cells_SepNormPCADf$cell_line == "WT",], aes(x = PC1, y = PC2,  color = Dose)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() +  xlim(-100, 70) + ylim(-110, 100) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("WT only WT Cis seperate Normalization") + guides(colour = guide_legend(override.aes = list(size=10)))

ggplot(WT_Cis_Cells_SepNormPCADf[WT_Cis_Cells_SepNormPCADf$cell_line == "Cis",], aes(x = PC1, y = PC2,  color = Dose)) + 
    geom_point(size= 2) + xlab(paste("PC1: Variance Explained = ", round(varExplained[1], 2), "%")) + theme_bw() +  xlim(-100, 70) + ylim(-110, 100) +
                               ylab(paste("PC2: Variance Explained = ", round(varExplained[2], 1), "%")) + ggtitle("Cis only WT Cis seperate Normalization") + guides(colour = guide_legend(override.aes = list(size=10))) 



```

## MOFA analysis

For MOFA analysis we'll set the cell paint features into different groups based on the organelle stained. Features that are not related to a particular stain (AreaShape, Nearest neighbours) will be put in their own group 
```{r}
require(MOFA2)
 smpN_Mofa <- 100
## Get the MOFA data sets
WT_Cis_Cells_CmbNorm_MOFA <- WT_Cis_CisplatinDoxUntreatedNrm[which(!grepl("Doxorubicin", WT_Cis_CisplatinDoxUntreatedNrm$Treatment)), ] %>% group_by(Dose, cell_line) %>% slice_sample(n = smpN_Mofa)

WT_CisCmbsMOFADat <- list()

summarizeLongFeat <- function(x){
  
  rownames(x) <- gsub("Granularity", "Grn", rownames(x))
  rownames(x) <- gsub("RadialDistribution", "RD", rownames(x))
  rownames(x) <- gsub("Texture", "Tx", rownames(x))
  rownames(x) <- gsub("Correlation", "Cr", rownames(x))
  rownames(x) <- gsub("InfoMeas", "InfM", rownames(x))
  rownames(x) <- gsub("Granularity", "Grn", rownames(x))
   rownames(x) <- gsub("CytoSkelCorr", "CySk", rownames(x))
   rownames(x) <- gsub("Intensity", "Inty", rownames(x))
  rownames(x) <- gsub("Difference", "Diff", rownames(x))
  rownames(x) <- gsub("Mitochondria", "Mito", rownames(x))
  rownames(x) <- gsub("AreaShape", "ArShp", rownames(x))
  x
  
}

# DNA parameters
WT_CisCmbsMOFADat$DNA <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("DNA_Corr")) %>% select(!matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$DNA) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$DNA <- summarizeLongFeat(WT_CisCmbsMOFADat$DNA)

# Cytoskeleton parameters
WT_CisCmbsMOFADat$Cyto <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("CytoSkelCorr"))%>% select(!matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$Cyto) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$Cyto <- summarizeLongFeat(WT_CisCmbsMOFADat$Cyto)

#rownames(WT_CisCmbsMOFADat$Cyto) <- myFun(nrow(WT_CisCmbsMOFADat$Cyto))

# ER parameters 
WT_CisCmbsMOFADat$ER <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("_ER_"))%>% select(!matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$ER) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$ER <- summarizeLongFeat(WT_CisCmbsMOFADat$ER)

# Mitochondria
WT_CisCmbsMOFADat$Mito <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("Mitochondria"))%>% select(!matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$Mito) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$Mito <- summarizeLongFeat(WT_CisCmbsMOFADat$Mito)

# AreaShapeNeighbour parameters
WT_CisCmbsMOFADat$AreaShape <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("AreaShape"))%>% select(!matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$AreaShape) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$AreaShape <- summarizeLongFeat(WT_CisCmbsMOFADat$AreaShape)

# Correlation parameters
WT_CisCmbsMOFADat$Correlation <- t((WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("^Correlation")))[,-1:-2])
colnames(WT_CisCmbsMOFADat$Correlation) <- paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))
WT_CisCmbsMOFADat$Correlation <- summarizeLongFeat(WT_CisCmbsMOFADat$Correlation)

# WT_CisCmbsMOFADat$ER <- t(WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("ER_Corr")))[-1:-2,]
# WT_CisCmbsMOFADat$Mito <- t(WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("Mitochondria_Corr")))[-1:-2,]
# WT_CisCmbsMOFADat$AreaShapeNeigh <- t(WT_Cis_Cells_CmbNorm_MOFA %>% select(matches("Neigh|AreaShape")))[-1:-2,]

## Make the MOFA object...

WT_CisCmbsMOFAobject <- create_mofa(WT_CisCmbsMOFADat)
WT_CisCmbsMOFAobject

## Plot the MOFA object
#plot_data_overview(WT_CisCmbsMOFAobject)

## Make options

model_opts <- get_default_model_options(WT_CisCmbsMOFAobject)

#model_opts$likelihoods["Mutations"] <- "bernoulli"

model_opts$num_factors <- 5

model_opts

## Prepare MOFA object
# WT_CisCmbsMOFAobject <- prepare_mofa(WT_CisCmbsMOFAobject,
#   model_options = model_opts
# )

## Write mofa object to rds
saveRDS(WT_CisCmbsMOFAobject, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/MOFA/cellPaintMOFA_071123.rds")


```
## Add the metadata
```{r}
WT_CisCmbsMOFA_meta <- cbind(data.frame(sample = paste0("Cell", 1:nrow(WT_Cis_Cells_CmbNorm_MOFA))),  WT_Cis_Cells_CmbNorm_MOFA[,metCols])
samples_metadata(WT_CisCmbsMOFAobject_Trained) <- data.table(WT_CisCmbsMOFA_meta)
```


## Get the MOFA objects
```{r}
WT_CisCmbsMOFAobject_Trained <- readRDS("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/MOFA/cellPaintMOFA_071123_trained.rds")

plot_variance_explained(WT_CisCmbsMOFAobject_Trained, max_r2=20)
```
## Correlate factors with covariates
```{r}
correlate_factors_with_covariates(WT_CisCmbsMOFAobject_Trained, 
  covariates = c("cell_line","Dose"), 
  plot = "log_pval"
  
)
```

## Factor loadings etc
```{r}
plot_weights(WT_CisCmbsMOFAobject_Trained,
 view = "Cyto",
 factor = 7,
 nfeatures = 20,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
```



## Get the top parameters from the PCA (well levl and cell level)
```{r}

## Well level ============================================================================================= ##
## WT/Cis individual normalization ------------------------------------------------------------------------ ##
# well_ind_nrm_low_PC1 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 1]))[1:10]
# well_ind_nrm_high_PC1 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 1]), decreasing = TRUE)[1:10]
# 
# well_ind_nrm_low_PC2 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 2]))[1:10]
# well_ind_nrm_high_PC2 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 2]), decreasing = TRUE)[1:10]
# 
# well_ind_nrm_low_PC3 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 3]))[1:10]
# well_ind_nrm_high_PC3 <- sort((WT_Cis_CisplatinUntreatedNrmMedPCA_IndividNrm$rotation[, 3]), decreasing = TRUE)[1:10]
# 
# ### get the features which are correlated
# correlatedFeaturesPC1_low_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_low_PC1)]
# correlatedFeaturesPC1_high_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_high_PC1)]
# 
# correlatedFeaturesPC2_low_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_low_PC2)]
# correlatedFeaturesPC2_high_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_high_PC2)]
# 
# correlatedFeaturesPC3_low_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_low_PC3)]
# correlatedFeaturesPC3_high_IndWell <- WT_Cis_CorrelatedFeatures_IndNrm[names(well_ind_nrm_high_PC3)]
# 
# ## WT+Cis combined normalization -------------------------------------------------------------------------- ##
# 
# well_cmb_nrm_low_PC1 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 1]))[1:10]
# well_cmb_nrm_high_PC1 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 1]), decreasing = TRUE)[1:10]
# 
# well_cmb_nrm_low_PC2 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 2]))[1:10]
# well_cmb_nrm_high_PC2 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 2]), decreasing = TRUE)[1:10]
# 
# well_cmb_nrm_low_PC3 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 3]))[1:10]
# well_cmb_nrm_high_PC3 <- sort((WT_CisplatinUntreatedNrmMedPCA_CmbNrm$rotation[, 3]), decreasing = TRUE)[1:10]
# 
# ### get the features which are correlated
# correlatedFeaturesPC1_low_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_low_PC1)]
# correlatedFeaturesPC1_high_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_high_PC1)]
# 
# correlatedFeaturesPC2_low_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_low_PC2)]
# correlatedFeaturesPC2_high_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_high_PC2)]
# 
# correlatedFeaturesPC3_low_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_low_PC3)]
# correlatedFeaturesPC3_high_cmbWell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(well_cmb_nrm_high_PC3)]

## Cell level ============================================================================================= ##
## WT/Cis individual normalization ------------------------------------------------------------------------ ##
cell_ind_nrm_low_PC1 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 1]))[1:10]
cell_ind_nrm_high_PC1 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 1]), decreasing = TRUE)[1:10]

cell_ind_nrm_low_PC2 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 2]))[1:10]
cell_ind_nrm_high_PC2 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 2]), decreasing = TRUE)[1:10]

cell_ind_nrm_low_PC3 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 3]))[1:10]
cell_ind_nrm_high_PC3 <- sort((WT_Cis_Cells_SepNormPCA$rotation[, 3]), decreasing = TRUE)[1:10]

correlatedFeaturesPC1_low_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_low_PC1)]
correlatedFeaturesPC1_high_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_high_PC1)]

correlatedFeaturesPC2_low_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_low_PC2)]
correlatedFeaturesPC2_high_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_high_PC2)]

correlatedFeaturesPC3_low_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_low_PC3)]
correlatedFeaturesPC3_high_Indcell <- WT_Cis_CorrelatedFeatures_IndNrm[names(cell_ind_nrm_high_PC3)]


pcIndFeatures <- unique(c(names(correlatedFeaturesPC1_low_Indcell), names(correlatedFeaturesPC2_low_Indcell), names(correlatedFeaturesPC3_low_Indcell),
                          names(correlatedFeaturesPC1_high_Indcell), names(correlatedFeaturesPC2_high_Indcell), names(correlatedFeaturesPC3_high_Indcell)))
                          


## WT+Cis combined normalization -------------------------------------------------------------------------- ##

cell_cmb_nrm_low_PC1 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 1]))[1:10]
cell_cmb_nrm_high_PC1 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 1]), decreasing = TRUE)[1:10]

cell_cmb_nrm_low_PC2 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 2]))[1:10]
cell_cmb_nrm_high_PC2 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 2]), decreasing = TRUE)[1:10]

cell_cmb_nrm_low_PC3 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 3]))[1:10]
cell_cmb_nrm_high_PC3 <- sort((WT_Cis_Cells_CmbNormPCA$rotation[, 3]), decreasing = TRUE)[1:10]

correlatedFeaturesPC1_low_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_low_PC1)]
correlatedFeaturesPC1_high_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_high_PC1)]

correlatedFeaturesPC2_low_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_low_PC2)]
correlatedFeaturesPC2_high_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_high_PC2)]

correlatedFeaturesPC3_low_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_low_PC3)]
correlatedFeaturesPC3_high_Cmbcell <- WT_Cis_CorrelatedFeatures_CmbNrm[names(cell_cmb_nrm_high_PC3)]

pcCmbFeatures <- unique(c(names(correlatedFeaturesPC1_low_Cmbcell), names(correlatedFeaturesPC2_low_Cmbcell), names(correlatedFeaturesPC3_low_Cmbcell),
                          names(correlatedFeaturesPC1_high_Cmbcell), names(correlatedFeaturesPC2_high_Cmbcell), names(correlatedFeaturesPC3_high_Cmbcell)))

```

## SOM for top features
```{r}
## Individual features ================================================================================================ ##
set.seed(222)
#g <- somgrid(xdim = 5, ydim = 5, topo = "rectangular")
g <- somgrid(xdim = 6, ydim = 6, topo = "rectangular")
WT_Cis_SOM36_Ind_TpFt <- som(as.matrix(WT_Cis_Cells_SepNorm[, pcIndFeatures]), grid = g)

plot(WT_Cis_SOM36_Ind_TpFt , type='codes', palette.name = rainbow)
plot(WT_Cis_SOM36_Ind_TpFt , type = "mapping")

SOM36_Values_NrmInd <- WT_Cis_SOM36_Ind_TpFt $codes[[1]]

## Combined features ================================================================================================ ##
set.seed(222)
#g <- somgrid(xdim = 5, ydim = 5, topo = "rectangular")
g <- somgrid(xdim = 6, ydim = 6, topo = "rectangular")
WT_Cis_SOM36_Cmb_TpFt <- som(as.matrix(WT_Cis_CisplatinDoxUntreatedNrm[!(WT_Cis_CisplatinDoxUntreatedNrm$Treatment == "Doxorubicin"), pcCmbFeatures]), grid = g)

plot(WT_Cis_SOM36_Cmb_TpFt , type='codes', palette.name = rainbow)
plot(WT_Cis_SOM36_Cmb_TpFt , type = "mapping")

SOM36_Values_NrmCmb <- WT_Cis_SOM36_Cmb_TpFt $codes[[1]]
```
## Cluster results
```{r}
## Individual normalisation

brkN <- 11
colors <- colorRampPalette(c("blue", "white","red"))(brkN)
breaks <- seq(-5, 5, length.out = brkN)

# consensusClust36FiltParmNodeCanberra <-  ConsensusClusterPlus(t(SOM36_Values_NrmInd),maxK=20,reps=50,pItem=0.8,pFeature=1, title="36 Node clustering",clusterAlg="hc",
#                                               seed=1262118388.71279, distance= "canberra", innerLinkage = "complete", finalLinkage = "complete")

pheatmap(SOM36_Values_NrmInd, show_colnames =  FALSE, breaks = breaks, color = colors, clustering_distance_rows = "canberra", main = "canberra 15", cutree_rows = 15)

## Combined normalization 
brkN <- 11
colors <- colorRampPalette(c("blue", "white","red"))(brkN)
breaks <- seq(-5, 5, length.out = brkN)

# consensusClust36FiltParmNodeCanberra <-  ConsensusClusterPlus(t(SOM36_Values_NrmInd),maxK=20,reps=50,pItem=0.8,pFeature=1, title="36 Node clustering",clusterAlg="hc",
#                                               seed=1262118388.71279, distance= "canberra", innerLinkage = "complete", finalLinkage = "complete")

pheatmap(SOM36_Values_NrmCmb, show_colnames =  FALSE, breaks = breaks, color = colors, clustering_distance_rows = "canberra", main = "canberra 15", cutree_rows = 15)


```

## Write top PCs to images
```{r}
nucLocs <- rbind(WT_CisplatinUntreated_nucLocs, Cis_CisplatinUntreated_nucLocs)

## Inidvidual norm ---------------------------------------------------------------------------------------------------------------------- ##
# ptchMetInd <- WT_Cis_Cells_SepNorm[, metCols]
# ptchMetInd$FilenameCyto <- gsub("UV - DAPI","Green - dsRed" , WT_Cis_Cells_SepNorm$FilenameDNA)
# 
# nucLocsInd <- dplyr::inner_join(ptchMetInd, nucLocs, by = c("FilenameDNA" = "FileName_DNA", "ObjectNumber_nuc" = "ObjectNumber_nuc"))
# 
# makeImagePatches(ptchMetInd, WT_Cis_SOM36_Ind_TpFt$unit.classif, nucLocsInd,
#                  '/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/IndNrm/',
#                  prefix = 'IndNrm', smpN = 30, setSeed = TRUE, seed = 47)

## COmbined norm ---------------------------------------------------------------------------------------------------------------------- ##

WT_Cis_CisplatinDoxUntreatedNrmNoDox <- WT_Cis_CisplatinDoxUntreatedNrm[!(WT_Cis_CisplatinDoxUntreatedNrm$Treatment == "Doxorubicin"), ]

ptchMet <- WT_Cis_CisplatinDoxUntreatedNrmNoDox[, metCols]
ptchMet$FilenameCyto <- gsub("UV - DAPI","Green - dsRed" , WT_Cis_CisplatinDoxUntreatedNrmNoDox$FilenameDNA)
#

nucLocs2 <- dplyr::inner_join(ptchMet, nucLocs, by = c("FilenameDNA" = "FileName_DNA", "ObjectNumber_nuc" = "ObjectNumber_nuc"))

makeImagePatches(ptchMet, WT_Cis_SOM36_Cmb_TpFt$unit.classif, nucLocs2,
                 "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/CmbNrm/",
                 prefix = "CmbNrm", smpN = 30, setSeed = TRUE, seed = 47)
```

## Get the composite images and the cell distributions

```{r}

## Cluster SOM nodes
xxNrmInd <- cutree(hclust(dist(SOM36_Values_NrmInd, "canberra")), k = 15)
xxNrmCmb <- cutree(hclust(dist(SOM36_Values_NrmCmb, "canberra")), k = 15)

## Plot the cluster composite images
compPlotsFromClusters("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/IndNrm/",
                      "IndNrm_", xxNrmInd,
                      "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/IndNrm/CompositeImages/")

compPlotsFromClusters("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/CmbNrm/",
                      "CmbNrm_", xxNrmCmb,
                      "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/CmbNrm/CompositeImages/")

 pltCellsInClusters(WT_Cis_Cells_SepNorm, SOM36_Values_NrmInd, WT_Cis_SOM36_Ind_TpFt$unit.classif, metCols, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/IndNrm/DoseDistributions//")
 
  pltCellsInClusters(WT_Cis_CisplatinDoxUntreatedNrmNoDox, SOM36_Values_NrmCmb, WT_Cis_SOM36_Cmb_TpFt$unit.classif, metCols, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_topPC_Parameters/CmbNrm/DoseDistributions///")

```

## SOM with Principle components
The individualy normed PCs are stored in variable: WT_Cis_Cells_IndNormPCA
The combined normed PCs are stored in the variable: WT_Cis_Cells_SepNormPCA

## SOM
```{r}
## Individually normed


```

## Hierachical clustering results
```{r}

```

## SOM
```{r}

## SOM with each cell line normed individually =============================================================== ##
# WT_Cis_CisplatinUntreatedNrm <- rbind(WT_CisplatinUntreatedNrm, Cis_CisplatinUntreatedNrm)
# 
# set.seed(222)
# #g <- somgrid(xdim = 5, ydim = 5, topo = "rectangular")
# g <- somgrid(xdim = 6, ydim = 6, topo = "rectangular")
# WT_Cis_FiltParmamSOM36_NrmInd <- som(as.matrix(WT_Cis_CisplatinUntreatedNrm[, datCols]), grid = g)
# 
# plot(WT_Cis_FiltParmamSOM36_NrmInd, type='codes', palette.name = rainbow)
# plot(WT_Cis_FiltParmamSOM36_NrmInd, type = "mapping")
# 
# SOM36_Values_NrmInd <- WT_Cis_FiltParmamSOM36_NrmInd$codes[[1]]
# 
# ## SOM with each cell line normed combined =============================================================== ##
# set.seed(222)
# #g <- somgrid(xdim = 5, ydim = 5, topo = "rectangular")
# #g <- somgrid(xdim = 6, ydim = 6, topo = "rectangular")
# WT_Cis_FiltParmamSOM36_NrmCmb <- som(as.matrix(WT_Cis_CisplatinDoxUntreatedNrm[, datCols]), grid = g)
# 
# plot(WT_Cis_FiltParmamSOM36_NrmCmb, type='codes', palette.name = rainbow)
# plot(WT_Cis_FiltParmamSOM36_NrmCmb, type = "mapping")
# 
# SOM36_Values_NrmCmb <- WT_Cis_FiltParmamSOM36_NrmCmb$codes[[1]]
# 
# #save(WT_Cis_FiltParmamSOM36_NrmInd, WT_Cis_FiltParmamSOM36_NrmCmb, WT_Cis_CisplatinUntreatedNrm, WT_Cis_CisplatinDoxUntreatedNrm, file = "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/RScripts_011122/SOM_Maps_NormedData_CisDOXUT.rdata")
# ```
# 
# ## Load data if needed
# ```{r}
# # load("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/RScripts_011122/RData/SOM_Maps_NormedData_CisDOXUT.rdata")
# ```
# 
# 
# ## Clustering and final outputs for individuallly normed samples
# ```{r}
# library(ConsensusClusterPlus)
# brkN <- 11
# colors <- colorRampPalette(c("blue", "white","red"))(brkN)
# breaks <- seq(-5, 5, length.out = brkN)
# 
# # consensusClust36FiltParmNodeCanberra <-  ConsensusClusterPlus(t(SOM36_Values_NrmInd),maxK=20,reps=50,pItem=0.8,pFeature=1, title="36 Node clustering",clusterAlg="hc",
# #                                               seed=1262118388.71279, distance= "canberra", innerLinkage = "complete", finalLinkage = "complete")
# 
# pheatmap(SOM36_Values_NrmInd, show_colnames =  FALSE, breaks = breaks, color = colors, clustering_distance_rows = "canberra", main = "canberra 15", cutree_rows = 15)
# 
# ## Make plots number of cells in clusters
# pltCellsInClusters(WT_Cis_CisplatinUntreatedNrm, SOM36_Values_NrmInd, WT_Cis_FiltParmamSOM36_NrmInd$unit.classif, metCols, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/Plots_NrmInd/")
#   
```

## Get plots for nrmCmb
```{r, fig.height=10}
# pheatmap(SOM36_Values_NrmCmb, show_colnames =  FALSE, breaks = breaks, color = colors, clustering_distance_rows = "canberra", main = "canberra 15", cutree_rows = 15)
# 
# xxNrmCmb <- hclust(dist(SOM36_Values_NrmCmb, "canberra"))
# yyNrmCmb <- cutree(xx, k = 15)
# 
# pheatmap(SOM36_Values_NrmInd, show_colnames =  FALSE, breaks = breaks, color = colors, clustering_distance_rows = "canberra", main = "canberra 15", cutree_rows = 15)
# 
# xxNrmInd <- hclust(dist(SOM36_Values_NrmInd, "canberra"))
# yyNrmInd <- cutree(xx, k = 15)

```


## 
```{r}
# 
# pltCellsInClusters(WT_Cis_CisplatinUntreatedNrm, SOM36_Values_NrmCmb, WT_Cis_FiltParmamSOM36_NrmCmb$unit.classif, metCols, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/Plots_NrmCmb/")
# 
# ## Make plots number of cells in clusters
# pltCellsInClusters(WT_Cis_CisplatinUntreatedNrm, SOM36_Values_NrmInd, WT_Cis_FiltParmamSOM36_NrmInd$unit.classif, metCols, "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/Plots_NrmInd/")

```


## Make image patches
```{r}
# ptchMet <- WT_Cis_CisplatinDoxUntreatedNrm[, metCols]
# ptchMet$FilenameCyto <- gsub("UV - DAPI","Green - dsRed" , WT_Cis_CisplatinDoxUntreatedNrm$FilenameDNA)
# 
# nucLocs <- rbind(WT_CisplatinUntreated_nucLocs, Cis_CisplatinUntreated_nucLocs)
# nucLocs2 <- dplyr::inner_join(ptchMet, nucLocs, by = c("FilenameDNA" = "FileName_DNA", "ObjectNumber_nuc" = "ObjectNumber_nuc"))

## NrmInd

# makeImagePatches(ptchMet, WT_Cis_FiltParmamSOM36_NrmInd$unit.classif, nucLocs2,
#                  "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/test/",
#                  prefix = "WT_Cis_16Bins_AreaShape_Radial16x1", smpN = 21, setSeed = TRUE, seed = 47)

## NrmCmb
# makeImagePatches(ptchMet, WT_Cis_FiltParmamSOM36_NrmCmb$unit.classif, nucLocs2,
#                  "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/test//",
#                  prefix = "WT_CisDOx", smpN = 3, setSeed = TRUE, seed = 147)

##
# compPlotsFromClusters("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/SOM_36_AllParNrmCmb/",
#                       "WT_CisDOx_", yyNrmCmb,
#                       "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/SOM_36_AllParNrmCmb/compIms/")
# 
# compPlotsFromClusters("/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/SOM_36_AllParNrmInd/", 
#                       "WT_Cis_16Bins_AreaShape_Radial16x1_", yyNrmInd, 
#                       "/data/CEAT/ImageDatasets/CellPaint_WTCis_EpiCompoundDoseResponse/R_Results/SOM_Predictions_CisDOXUT/SOM_36_AllParNrmInd/compIms/")
```

## Well locations of cell groups
```{r}

## Need cell locations and Cluster class
# nucLocs2$Metadata_Field <- (nucLocs2$FilenameDNA)


```

